Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 Discussion.tex
got rid of ugly expressions
fixed typos in 4, 4.4
significant edits throughout

When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
\end{itemize}

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right).  \nonumber
\end{align}
\end{theorem}

@@

When this assumption holds, we choose a different modification in the definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

This, knowledge of \MinProb allows the algorithm to incentivize significantly fewer arm pulls.
We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in the Appendix~\ref{sec:discussion-proof2}.

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and an expected regret bounded above by
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
\end{theorem}

>>>>

When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
\end{itemize}

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{theorem}

@@

When this assumption holds, we choose a different modification in the definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

This knowledge of \MinProb allows the algorithm to incentivize
significantly fewer arm pulls.
We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
\end{theorem}

### 2018-06-05 Lemmas.tex
significant edits throughout

\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
\label{lem:ACI-inequality}
Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
(We allow $J$ to take the value $\infty$,
defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
Define 
$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
Then, 
$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
\end{lemma}

@@

By Assmption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

>>>>

\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
\label{lem:ACI-inequality}
Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
(We allow $J$ to take the value $\infty$,
defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
Define 
$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.

Then, 
$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
\end{lemma}

@@

By Assmption~\ref{A1}
\dkedit{(including that $\frac{\MinProb}{2\TieDensity} \leq \TieCutoff$)},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

### 2018-06-05 abstract.tex
significant edits throughout

We consider the problem of incentivizing exploration with heterogeneous agents.
In this problem, bandit arms provide vector-valued outcomes equal to an unknown
arm-specific attribute vector,
perturbed by independent noise.
Agents arrive sequentially and choose arms to pull based on their own
private and heterogeneous linear utility functions over attributes
and the estimates of the arms' attribute vectors derived from
observations of other agents' past pulls.
Agents are myopic and selfish and thus would choose the arm with
maximum estimated utility.
A principal, knowing only the distribution from which agents'
preferences are drawn, but not the specific draws,
can offer incentive payments for pulling specific arms
in order to encourage agents to explore underplayed arms.
The principal seeks to minimize the total expected cumulative regret
incurred by agents relative to their best arms,
while also making a small expected cumulative payment.

>>>>

We consider the problem of incentivizing exploration with heterogeneous agents.
In this problem, \dkedit{\ARMNUM} bandit arms provide vector-valued outcomes equal to an unknown
arm-specific attribute vector,
perturbed by independent noise.
Agents arrive sequentially and choose arms to pull based on their own
private and heterogeneous linear utility functions over attributes
and the estimates of the arms' attribute vectors derived from
observations of other agents' past pulls.
Agents are myopic and selfish and thus would choose the arm with
maximum estimated utility.
A principal, knowing only the distribution from which agents'
preferences are drawn, but not the specific draws,
can offer incentive payments for pulling specific arms
in order to encourage agents to explore underplayed arms.
The principal seeks to minimize the total expected cumulative regret
incurred by agents relative to their best arms,
while also making a small expected cumulative payment.

### 2018-06-05 algorithm_general.tex
significant edits throughout

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.

@@

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have 
$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
\end{lemma}

Next, we show the complementary result:
when event \AccEU{t}{x} happens, no myopic agent incurs large regret.

>>>>

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.
\dkcomment{If we only get 12 pages in the proceedings, make sure to
  replace ``appendix'' by ``online appendix'' or ``supplemental
  material'' or whatever we call it, here and everywhere else.}

@@

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\dkedit{\tau_s} \in [t_s, t_{s+1})$ almost surely.
\dkcomment{$\tau$ was missing the subscript $s$ here. I think that was
  a mistake, but am marking it so someone can check.}
Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have 
$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
\end{lemma}

Next, we show the complementary result:
when the event \AccEU{t}{x} happens, no myopic agent incurs large regret.

### 2018-06-05 algorithm_intro.tex
significant edits throughout

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free''.}
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be an arbitary payment-eligible arm.
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $x$ or better.
Then, 
$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $x$ simultaneously.
We will then show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{x})
have high probability,
and that when they do, myopic agents do not make large mistakes.

>>>>

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given the current estimates \ArmEV{t}{i'} of the arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free.''}
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be an arbitary payment-eligible arm.
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $x$ or better.
Then, 
$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $x$ simultaneously.
We will show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{x})
have high probability,
and that when they do, myopic agents do not make large mistakes.

### 2018-06-05 algorithm_payment.tex
significant edits throughout

Towards bounding the algorithm's total payment, we now bound the
\emph{number} of rounds in which the algorithm makes a payment by a
constant.
This bound also turns out to be useful for bounding the total regret.

@@

Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurred before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

>>>>

Towards bounding the algorithm's total payment, we now bound by a
constant the \emph{number} of rounds in which the algorithm makes a
payment.
This bound also turns out to be useful for bounding the total regret.

@@

Fix an arm $i$, and consider the \Kth{s} pull of arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurred before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

### 2018-06-05 algorithm_regret.tex
significant edits throughout

We distinguish between agents incurring large regret
(which requires severe misestimates of arm locations;
such misestimated are exponentially unlikely to occur), 
and agents incurring small positive regret,
which requires these agents to be almost tied in their preference for
the best arm.
To be more precise, we will define (with foresight) a phase-dependent
cutoff
$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
and consider a regret exceeding $g(s)$ large.

We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Assumption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each incurs regret at most $g(s)$.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
regret more than $g(s)$.

@@

Adding all three types of regret terms,
and substituting that 
$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)
& = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}

>>>>

We distinguish between agents incurring large regret
(which requires severe misestimates of arm locations;
such misestimates are exponentially unlikely to occur), 
and agents incurring small positive regret,
which requires these agents to be almost tied in their preference for
the best arm.
To be more precise, we define (with foresight) a phase-dependent
cutoff
$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
and consider a regret exceeding $g(s)$ large.

\dkedit{
For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.
Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}

\dkedit{For the remainder of the proof, we consider phases $s$
with $g(s) \leq \TieCutoff$.}
We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Assumption~\ref{A1}, \dkedit{and because $g(s) \leq \TieCutoff$,}
%Lemma~\ref{lem:sdelta},
the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each such agent incurs regret at most $g(s)$.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$.
\dkcomment{We have already used $t_s$ before, e.g., in the preceding
  formula. Do we need to redefine it here?}
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
regret more than $g(s)$.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining $g(s)$ to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}

@@

Adding all \dkedit{four} types of regret terms,
and substituting that 
$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
\dkedit{+ \ARMNUM \MAXR \log^2(T)}
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
\\ & = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}

### 2018-06-05 colt.tex
fixed the format
addressing modeling questions
significant edits throughout

\documentclass[twoside,11pt]{article}
\usepackage[anon]{jmlr2e}

@@

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}

% Short headings should be running head and authors last names

\ShortHeadings{Incentivizing Exploration with Heterogeneous Utilities}{Chen, Frazier and Kempe}
\firstpageno{1}

@@

\title{Incentivizing Exploration by Heterogeneous Users}

\author{\name Bangrui Chen \email bc496@cornell.edu \\
\name Peter I.\ Frazier \email pf98@cornell.edu \\
\addr Operations Research and Information Engineering\\
Cornell University\\
New York, NY 14850, USA
\AND
\name David Kempe \email david.m.kempe@gmail.com  \\
\addr Department of Computer Science\\
University of Southern California\\
Los Angeles, CA 90089, USA}

\editor{}

@@

\begin{abstract}
\input{abstract.tex}
\end{abstract}

@@

\newpage

@@

\bibliography{reference}
\end{document}

>>>>

\documentclass[final,12pt]{colt2018}
% \usepackage[anon]{jmlr2e}

@@

\title{Incentivizing Exploration by Heterogeneous Users}
\usepackage{times}

\coltauthor{\Name{Bangrui Chen} \Email{bc496@cornell.edu} \\
\Name{Peter I.\ Frazier} \Email{pf98@cornell.edu} \\
\addr Operations Research and Information Engineering\\
Cornell University\\
New York, NY 14850, USA
\AND
\Name{David Kempe} \Email{david.m.kempe@gmail.com}  \\
\addr Department of Computer Science\\
University of Southern California\\
Los Angeles, CA 90089, USA}

@@

@@

\begin{abstract}
\dkcomment{Should we be changing the ``Proveedings of ...'' part on
  the top?}

\input{abstract.tex}
\end{abstract}

@@

\acks{PF and BC were partially supported by NSF CMMI-1254298 and AFOSR
FA9550-15-1-0038.
DK was supported in part by NSF grant 1423618.}

\bibliography{reference}

@@

\end{document}

### 2018-06-05 conclusion.tex
significant edits throughout

\section{Conclusion}
We study the problem of incentivizing exploration with heterogeneous
user preferences.
We proposed an algorithm that achieves expected cumulative regret of
$O(\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
It is possible to improve these bounds to polynomial (in \ARMNUM and
$1/\MinProb$) when \MinProb is known or the preference distribution is
discrete.
In fact, we conjecture that this should be possible even in the full
generality of our model.
As a first step towards such a polynomial bound, we believe that it
should be possible to obtain an exponential dependence on
$1/(\MinProb \ARMNUM)$, which gives polynomial dependence unless some
arm has a much smaller fraction of the population preferring it.

>>>>

\section{Conclusion}
We study the problem of incentivizing exploration with heterogeneous
user preferences.
We proposed an algorithm that achieves expected cumulative regret
$O(\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
It is possible to improve these bounds to polynomial (in \ARMNUM and
$1/\MinProb$) when \MinProb is known or the preference distribution is
discrete.
In fact, we conjecture that this should be possible even in the full
generality of our model.
As a first step towards such a polynomial bound, we believe that it
should be possible to obtain an exponential dependence on
$1/(\MinProb \ARMNUM)$, which gives polynomial dependence unless some
arm has a much smaller fraction of the population preferring it.
